Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data

### 2021-08-05 paper.Rmd
Bugfix in paper.Rmd

---
title: "Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
  - name: Doris Oriwol
    email: doris.oriwol@partner.kit.edu
    affiliation: Karlsruhe Institute of Technology
  - name: Christian Maiwald
    email: christian.maiwal@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
# address:
#   - code: Chemnitz University of Technology
#     address:  Thüringer Weg 11, 09126 Chemnitz
#   - code: Another University
#     address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v1 <- crossval_coverage(data, n.boot, method = "all", ver = "v1")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v2 <- crossval_coverage(data, n.boot, method = "all", ver = "v2")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v3 <- crossval_coverage(data, n.boot, method = "all", ver = "v3")

>>>>

---
title: "Asymmetric functional prediction bands for assessing the validity of spatiotemporally smooth biomechanical curve data"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
  - name: Doris Oriwol
    email: doris.oriwol@partner.kit.edu
    affiliation: Karlsruhe Institute of Technology
  - name: Christian Maiwald
    email: christian.maiwald@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
# address:
#   - code: Chemnitz University of Technology
#     address:  Thüringer Weg 11, 09126 Chemnitz
#   - code: Another University
#     address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v1 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v1")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v2 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v2")

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
cover.cross.v3 <- crossval_coverage(data, floa, floa.point, method = "all", ver = "v3")
